A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-12-17 writedown/zm/paper.water/main.tex
my revise

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Monday, December 01, 2014 18:07:38}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}

\begin{document}

@@

In order to investigate the physical-chemical properties obtained  by ZMM, we simulate the water
system by using both SPME and ZMM, and evaluate a set of \emph{%
benchmark quantities}. This set covers a broad range of water properties
that are of general interest. It includes the structure property (radial
distribution function), the thermodynamic properties (pressure, excess
chemical potential, constant volume/pressure heat capacity, isothermal
compressibility, thermal expansion coefficient), dielectric properties
(dielectric constant and Kirkwood-G factor) and dynamical properties
(diffusion constant and viscosity). The definitions and computing methods of
these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZMM to SPME, a good consistency in
computing the benchmark quantities should indicate a good accuracy of the ZMM.
More importantly, the benchmark tests provide knowledge in the
situations when the ZMM does not work so well, and help in finding the
way of tuning the working parameters to achieve higher accuracy. The ZMM
is also compared to the traditional short-range method: RF.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZMM
  with order from 1 to 4 are compared with the RF. The splitting
parameter of ZMM  is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.}
% [ {\ 
% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
% \color{blue} another COMMENT: In these figures, can we see the statistical
% uncertainty of the pressure obtained by the SPME? Viz., I found no error
% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
% is the target pressure.}][{\color{blue} Can I konw the the statistical
% uncertainty of the pressure obtained by the SPME?}]
}
\label{fig:pres-comp}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZMM
of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
are plotted in Fig.~\ref{fig:pres-comp}. All ZMM  converges to
the target pressure at large enough cut-off radius. Lower order ZMM presents
an smaller error in the pressure calculation than the higher order ZMM.
Note ZMM $l=1$ tends to under-estimate the pressure, while ZMM $l=2,3$
and 4 tends to over-estimate. However, the accuracy of ZMM in pressure
calculation is much higher than that of the RF.

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{ The pressure convergence with respect to the cut-off radius for ZMM
  $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,\text{nm}^{-1}$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}. 
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZMM~\cite{fukuda2014zero}. The convergence is not
sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.  In practice a
pressure error of 20~Bar will only cause a density deviation (calculated by
the NPT simulations) of roughly 0.1\%. Taking different orders ZMM  at
cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
pressure error is less than 20~Bar, while for $l=4$ the pressure error is
less than 30~Bar (see Fig.~\ref{fig:pres-comp}).

% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
% It will show that the fluctuation is large and the 10 Bar error for ZMM looks
% small. If there is a suitable one, it may be good to put it in SI.} {%
% \color{red} Could you explain why? The SD should be enough for our purpose.}%
% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
% Some potential users of ZMM\ may worry about the deviation of the density
% from the reality due to the pressure error. I remember that the density
% error for ZMM was small. It is helpful to show that the deviation of the
% density is sufficiently small. These two comments indicates that one wants
% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
% \color{blue} Thank you very much for your consideration of the density. {%
% COMMENT1: please see my question in the last page. COMMENT2: The deviation
% of the pressure between the ZMM and PME should be due to this density
% deviation between the ZMM and PME (0.1\%). Namely {0.1\% density deviation
% should cause 10 atm deviation.}\ How about this confirmation? ---The
% pressure by ZMM\ in figs1\&2 was calculated with the NTV MD where the cell
% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
% the cell size determined by the \textit{ZMM} NTP (which was used to calculate
% the current density), and if we calculate the pressure by ZMM with this new
% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
% true, then we can show that the 10 atm deviation from the PME is not the
% serious problem but a tiny density deviation issue.--- How about this idea? }%
% }]

% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
is qualitatively wrong, and the accuracy of the ZMM  is much
higher. In the system of smaller size ($M_{1}$), ZMM  of all orders are
highly consistent with the SPME result, and $l=2$ gave the best result. In the
system of larger size ($L_{1}$), the accuracies of the ZMM  is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZMM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. The
Kirkwood-G factor computed by ZMM in system $S_{1}$ is as good as that
computed in $M_{1}$, and is presented in SI.

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
order of ZMM  is $l=3$. The splitting parameter is $\protect\alpha %
=0.0\,\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
confidence level by the error bars. }
\label{fig:gkr-conv}
\end{figure}

@@

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZMM  of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1},
it shows that in the case of $l=1$, the largest splitting parameter ($\alpha
=2.0\ \text{nm}^{-1}$) is worse in calculating the Kirkwood-G factor than
smaller splitting parameters. Splitting parameter dependency was not so
clear for $l=2$ and 3 (shown in SI). Note that in many cases the
discrepancies from the SPME were relatively prominent in the middle range of
the distance and they tend small for larger distance.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(T)$. Different orders of ZMM  are compared with the SPME
as well as RF results. The error bars indicating 95\% confidence level are
plotted with the SPME method. }
\label{fig:conv-vis}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(T)$. Different splitting parameters for ZMM order $l=1$ are
plotted. The error bars indicating 95\% confidence level are plotted with
the SPME method. }
\label{fig:conv-vis-damp}
\end{figure}

Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
RF  converges at 6~ps, while the ZMM  converges only in 2~ps,
which is consistent with the SPME result. The value of ZMM $l=1$  is
different from the rest ZMM  and SPME result, but the results was
improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.
Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the convergence is
quick for a large $\alpha $.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-rdf.eps}
\caption{The comparison of the center-of-mass radial distribution functions
calculated by SPME, ZMM and RF. The insert is a zoom-in of range 0.9
-- 1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated
by a vertical black line. For ZMM, the splitting parameter $\protect%
\alpha $ was set to 0.0~$\text{nm}^{-1}$. }
\label{fig:rdf}
\end{figure}

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZMM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF. It is observed from the figure that the
ZMM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and $%
{0.3\%}$ for $l=2$, % {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order ZMM present lower
amplitude oscillation, and when $l\geq 3$, the improvement is dramatic and
the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZMM ones,
this is mainly because of the group cut-off used in simulating with RF. When changing
the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZMM $l=1$ (see SI).
We could not explain the reason, but the numerical evidence suggests if only the RDF is
of interest, a group cut-off scheme or higher order of ZMM is preferable.
}

@@

The oscillations for $l=1$\ can also be substantially improved by using a
larger splitting parameter $\alpha $. Figure~\ref{fig:rdf-damp} presents the
RDF of ZMM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}^{-1}$%
. The damping effect, viz., a clear trend of better RDF by using a larger $%
\alpha $, is observed. At $\alpha =2.0\ \text{nm}^{-1}$ the RDF is almost
overlapping with the SPME result. This damping effect is clearer for a
smaller order $l$\ (see SI for results of {$l=2$ and $3$}), as expected from
the pair potential behavior~\cite{fukuda2014zero}.

@@

>>>>

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Wednesday, December 10, 2014 19:23:08}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
% \input{tcilatex}
\begin{document}

@@

In order to investigate the physical-chemical properties obtained by ZMM, we
simulate the water system by using both SPME and ZMM, and evaluate a set of 
\emph{benchmark quantities}. This set covers a broad range of water
properties that are of general interest. It includes the structure property
(radial distribution function), the thermodynamic properties (pressure,
excess chemical potential, constant volume/pressure heat capacity,
isothermal compressibility, thermal expansion coefficient), dielectric
properties (dielectric constant and Kirkwood-G factor) and dynamical
properties (diffusion constant and viscosity). The definitions and computing
methods of these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZMM to SPME, a good consistency in
computing the benchmark quantities should indicate a good accuracy of the
ZMM. More importantly, the benchmark tests provide knowledge in the
situations when the ZMM does not work so well, and help in finding the way
of tuning the working parameters to achieve higher accuracy. The ZMM is also
compared to the traditional short-range method: RF. Magnitude
of the deviations between the ZMM and SPME is basically
discussed considering the statistical uncertainty.  \recheck{More details of the statistical
uncertainty in computing a physical quantity is provided in Appendix~\ref{app:error}.}
% ....[COMMENTS: Since the critical issue of this ms is the
% accuracy check, it is helpful (around here) to describe briefly how this
% check is done. This is also helpful for readers to understand the PME\
% pressure deviation "($-0.4\pm 1.5$~Bar){" appearing later. A little bit more
% detailed descriptions may be added in Appendix. Duplication to the caption
% of fig 1 is not the problem.]} }

@@

\begin{figure}[tbp]
\caption{The pressure convergence with respect to the cut-off radius. The
ZMM with order from 1 to 4 are compared with the RF. The splitting parameter
of ZMM is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$. The black solid
line indicates the magnitude of the correct pressure: 1~Bar. The error bars
present the statistical uncertainty at 95\% confidence level. {\color{red}
This uncertainty is twice of the standard deviation of the estimates (which
are averages along MD trajectories) that is calculated by the block average
method~\protect\cite{janke2002statistical}.} }
\label{fig:pres-comp}\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZMM of
order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF are plotted in
Fig.~\ref{fig:pres-comp}. All ZMM converges to the target pressure at large
enough cut-off radius. Lower order ZMM presents an smaller error in the
pressure calculation than the higher order ZMM. Note ZMM $l=1$ tends to
under-estimate the pressure, while ZMM $l=2,3$ and 4 tends to over-estimate.
However, the accuracy of ZMM in pressure calculation is much higher than
that of the RF. 
\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{ The pressure convergence with respect to the cut-off radius for
ZMM $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The
black solid line indicates the magnitude of the correct pressure: 1~Bar. The
error bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}
The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,%
\text{nm}^{-1}$ should be used in the simulations where the high accuracy in
the pressure is important. This "anti-damping effect" is similarly seen in
the energy accuracy in the TIP3P model~\cite{fukuda2014zero}. 
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZMM~\cite{fukuda2014zero}. The convergence is not
sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.

{Larger estimations of the pressure seen in the ZMMs with $l>1$
should come from, roughly speaking, the suppression of the negative
contribution of the dipole-dipole (Keesom) attractive interaction from a
long distance. The suppression is larger, as the values of ${l}$ and $\alpha 
$ increase due to the damping in the ZMM pair function, and larger as $r_{%
\text{c}}$ decreases. Specifically, the ignorance of the Fourier part in the
ZMM~\cite{fukuda2011molecular} accounts for this suppression, since
suppressed function erf$(\alpha r)/r$ tends to the original Coulomb $1/r$ as 
$\alpha $ increases (e.g., erf$(\alpha r)\sim 1$ for $\alpha r\gtrsim 2$).
Thus the ignorance causes positive contribution to the pressure estimation
with increasing $\alpha $, as observed in Fig.~\ref{fig:pres-l1}. This
ignorance is validated for a small} { $\alpha $, which limits
the use of large $\alpha $\ in the ZMM. In addition, the dependence on order 
$l$ should be relevant to the excess energy error~\cite{fukuda2014zero},
which depends on the order. }

{The magnitude and origin of the deviations of the pressure in
the ZMM\ are discussed more quantitatively. First note that even with the
largest} system $L_{0}$ that contains 13824 water molecules, the fluctuation
(measured by standard deviation) of the pressure is roughly 100~Bar {%
(see SI fig.1)}, which means that it is very difficult to
achieve very accurate estimate for this quantity. {A pressure
error of 20~Bar only cause a density deviation, which is calculated by the
NPT simulations of ZMM, of roughly }${0.1}${\% (The density
deviation of ${0.1}$\% corresponds to each cell length deviation of about $%
0.03$\%, which should not be important to many applications). In fact,}
taking different orders ZMM at cut-off 1.2~nm with $\alpha =0$%
 for example, the density deviations {were} $0.051$\%, 
$0.061$\%, $0.097$\% and $0.146$\% for $l=1,2,3$ and 4, respectively.
%For $l\leq 3$ the pressure error is less than 20~Bar, while
%for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref%
%{fig:pres-comp}).
% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
% It will show that the fluctuation is large and the 10 Bar error for ZMM looks
% small. If there is a suitable one, it may be good to put it in SI.} {%
% \color{red} Could you explain why? The SD should be enough for our purpose.}%
% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
% Some potential users of ZMM\ may worry about the deviation of the density
% from the reality due to the pressure error. I remember that the density
% error for ZMM was small. It is helpful to show that the deviation of the
% density is sufficiently small. These two comments indicates that one wants
% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
% \color{blue} Thank you very much for your consideration of the density. {%
% COMMENT1: please see my question in the last page. COMMENT2: The deviation
% of the pressure between the ZMM and PME should be due to this density
% deviation between the ZMM and PME (0.1\%). Namely {0.1\% density deviation
% should cause 10 atm deviation.}\ How about this confirmation? ---The
% pressure by ZMM\ in figs1\&2 was calculated with the NTV MD where the cell
% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
% the cell size determined by the \textit{ZMM} NTP (which was used to calculate
% the current density), and if we calculate the pressure by ZMM with this new
% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
% true, then we can show that the 10 atm deviation from the PME is not the
% serious problem but a tiny density deviation issue.--- How about this idea? }%
% }]
{Namely, the density of
the current simulation was fixed by the SPME NPT simulation, and this
density was deviated about $0.1$\% from the equilibrated value of the ZMM.} {%
The pressure deviations of the ZMM, although which may seem
large, originated from this slight density deviations between the SPME and
ZMM and from the sensitivity of the pressure to the density.} 
% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
is qualitatively wrong, and the accuracy of the ZMM is much higher. In the
system of smaller size ($M_{1}$), ZMM of all orders are highly consistent
with the SPME result, and $l=2$ gave the best result. In the system of
larger size ($L_{1}$), the accuracies of the ZMM is less for order $l\geq 2$%
, while they may be in still acceptable accuracy. In both systems, ZMM $l=1$
presents an artificial oscillation around the cut-off radius (1.2~nm), while
this oscillation is not obvious for $l\geq 2$. The Kirkwood-G factor
computed by ZMM in system $S_{1}$ is as good as that computed in $M_{1}$,
and is presented in SI.

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
order of ZMM is $l=3$. The splitting parameter is $\protect\alpha =0.0\,%
\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
confidence level by the error bars. }
\label{fig:gkr-conv}
\end{figure}

@@

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZMM of order $l=3$.
Without surprising, the Kirkwood-G factor converges to the SPME result when
using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1}, it
shows that in the case of $l=1$, the largest splitting parameter ($\alpha
=2.0\ \text{nm}^{-1}$) is worse in calculating the Kirkwood-G factor than
smaller splitting parameters. Splitting parameter dependency was not so
clear for $l=2$ and 3 (shown in SI). Note that in many cases the
discrepancies from the SPME were relatively prominent in the middle range of
the distance and they tend small for larger distance.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(t)$. Different orders of ZMM are compared with the SPME as
well as RF results. The error bars indicating 95\% confidence level are
plotted with the SPME method. }
\label{fig:conv-vis}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(t)$. Different splitting parameters for ZMM order $l=1$ are
plotted. The error bars indicating 95\% confidence level are plotted with
the SPME method. }
\label{fig:conv-vis-damp}
\end{figure}

Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
RF converges at 6~ps, while the ZMM converges only in 2~ps, which is
consistent with the SPME result. The value of ZMM $l=1$ is different from
the rest ZMM and SPME result, but the results was improved by the damping
effect as shown in Fig.~\ref{fig:conv-vis-damp}. Similar to the behaviors
seen in Fig.~\ref{fig:conv-vis}, the convergence is quick for a large $%
\alpha $.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-rdf.eps}
\caption{The comparison of the center-of-mass radial distribution functions
calculated by SPME, ZMM and RF. The insert is a zoom-in of range 0.9 --
1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated by a
vertical black line. For ZMM, the splitting parameter $\protect\alpha $ was
set to 0.0~$\text{nm}^{-1}$. }
\label{fig:rdf}
\end{figure}

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZMM ($l=1,2,3$ and $%
4 $) with $\alpha =0$\ and RF. It is observed from the figure that the ZMM
RDFs are consist very well with the SPME RDF, except oscillations around the
cut-off radius. This oscillations are not so large, as the maximum magnitude
of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and ${0.3\%}$
for $l=2$, % {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order ZMM present lower amplitude
oscillation, and when $l\geq 3$, the improvement is dramatic and the
oscillation is almost negligible. [ {\color{blue}COMMENT: I thank for your
efforts to reveal that the GC is far better than AC in RDF. Complete pursuit
of RF RDF, including the verification of Prof Nakamura's scenario, should be
our future work. Thus I have omitted the descriptions of the difference
between GC and AC in RDF]} %{\color{red} The RF RDF is more accurate
%than the ZMM ones, this is mainly because of the group cut-off used in
%simulating with RF. When changing the cut-off scheme to atom scheme, the
%accuracy is RF is roughly same as ZMM $l=1$ (see SI). We could not explain
%the reason, but the numerical evidence suggests if only the RDF is of
%interest, a group cut-off scheme or higher order of ZMM is preferable. }

@@

The oscillations for $l=1$\ can also be substantially improved by using a
larger splitting parameter $\alpha $. Figure~\ref{fig:rdf-damp} presents the
RDF of ZMM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}%
^{-1} $. The damping effect, viz., a clear trend of better RDF by using a
larger $\alpha $, is observed. At $\alpha =2.0\ \text{nm}^{-1}$ the RDF is
almost overlapping with the SPME result. This damping effect is clearer for
a smaller order $l$\ (see SI for results of {$l=2$ and $3$}), as expected
from the pair potential behavior~\cite{fukuda2014zero}.

@@

\section{The definition of statistical uncertainty of a physical quantity}
\label{app:error}
